Ứng Dụng Dữ Liệu Lớn và Quản Lý Tài Sản Hạ Tầng Trong Ngành Điện Lực

### 2023-03-17 2023-EVN-Data-Analytics-for-CEO/paper/paper.tex
update

\title[Dữ Liệu Lớn/Quản Lý Hạ Tầng - Điện Lực]{Dữ Liệu Lớn và Quản Lý Hạ Tầng Trong Ngành Điện Lực}

@@

\section*{Lời Cám Ơn}
This is a short text to acknowledge the contributions of specific colleagues, institutions, or agencies that aided the efforts of the authors.

>>>>

\title[Ứng Dụng Dữ Liệu Lớn/Quản Lý Hạ Tầng - Điện Lực]{Ứng Dụng Dữ Liệu Lớn và Quản Lý Tài Sản Hạ Tầng Trong Ngành Điện Lực}

@@

\section{Quản Lý Tài Sản Hạ Tầng}

\section{}

%\section*{Lời Cám Ơn}
%This is a short text to acknowledge the contributions of specific colleagues, institutions, or agencies that aided the efforts of the authors.
